Investigating Biases Associated with Dietary Starch Incorporation and Retention with an Oral Biofilm Model

### 2023-02-09 analysis/paper/paper.Rmd
add call to load functions

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  #fig.path = "frontiers/figures/",
  fig.path = "../figures/",
  fig.align = "center",
  #fig.ext = "jpg",
  fig.pos = "H",
  dpi = 300) 
library(dplyr)
library(ggplot2)
library(broom)
library(here)
library(patchwork)
plt1_ph1 <- readr::read_tsv(
  here("analysis/data/raw_data/ExpM_plate1_photometric1.csv"),
  col_names = F)
plt1_ph2 <- readr::read_tsv(
  here("analysis/data/raw_data/ExpM_plate1_photometric2.csv"),
  col_names = F)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  #fig.path = "frontiers/figures/",
  fig.path = "../figures/",
  fig.align = "center",
  #fig.ext = "jpg",
  fig.pos = "H",
  dpi = 300) 
library(dplyr)
library(ggplot2)
library(broom)
library(here)
library(patchwork)
devtools::load_all()
plt1_ph1 <- readr::read_tsv(
  here("analysis/data/raw_data/ExpM_plate1_photometric1.csv"),
  col_names = F)
plt1_ph2 <- readr::read_tsv(
  here("analysis/data/raw_data/ExpM_plate1_photometric2.csv"),
  col_names = F)
